The field of multi-target tracking (MTT) faces two primary challenges: (i) data association and (ii) trajectory estimation. Many algorithms, such as the MHT and JPDAF, attempt to solve the MTT problem via probabilistic approaches, while few employ the use of optimization models. In this paper we take a new approach to the MTT problem by modeling it as a mixed integer optimization (MIO) model, making no probabilistic assumptions on the data. We model the basic case where there is no detection ambiguity, \textit{i.e.}, no false alarms or missed detections, and extend it to the more difficult robust case where there exists detection ambiguity. These models solve the data association and trajectory estimation problems simultaneously by minimizing an easily interpretable global objective function. Additionally, we propose a greedy heuristic that scales efficiently and finds high quality solutions in milliseconds, and we show that these heuristic solutions can be used effectively as a warm start for the MIO, enabling the MIO to achieve good solutions in seconds. In the basic case, the model has no tunable parameters and the extension to the ambiguous case requires only two easily understood parameters which serve as objective function penalties. Furthermore, we introduce a new metric for measuring complexity in the data association problem as well as a metric for measuring the performance of trajectory estimation. Numerical results show that in the case of the basic model we obtain a good reconstruction of the original tracks for a range of scenarios, while in the robust case, for small to medium sized scenarios we are able to both estimate the correct number of targets as well as correctly reconstruct the trajectories.