I would like to thank everyone who played a role in making this opportunity possible, everyone who supported me throughout this process, and everyone who influenced this project in any manner. Though I unfortunately do not have the space to thank each of you by name, I am immensely grateful for each and every one of you and the impacts you have had on me and this work. 

I would like to thank my advisor, Professor Dimitris Bertsimas, for his ongoing support and
guidance throughout this project. Without your direction and ideas none of this would have been possible. I thank you for constantly challenging me to push myself and for propelling me to expand my academic prowess beyond what I could have thought possible for myself. Additionally, I would like to thank Shimrit Shtern for her guidance and counseling on this project as well. Thank you for taking the time to pour over my error ridden scripts, edit this paper, and provide further guidance at critical points of this project. 

Thank you to everyone at Lincoln Laboratories who played a role in making this degree possible. To Mr John Kuconis, thank you for facilitating this opportunity and generously sponsoring me through a military fellowship. To my advisor, Sung-Hyun Son, I also want to thank you for providing me the opportunity to be a Lincoln Laboratory Military Fellow in Group 36. Additionally, thank you for introducing me to the MTT problem and encouraging me to explore a field of the Air Force that was new to me, something that will no doubt pay dividends in my future as an officer in the Air Force. To Steve Relyea, thank you for meeting with me regularly and helping me weed through the details of the MTT problem, repeatedly scratching out ideas on paper. Your advice and insight was critical to both getting this project up and running and keeping it on track throughout the process. Furthermore, I would like to thank the Lincoln Laboratories LLGrid team for their support in running my experiments. As a first time Linux user, your assistance was instrumental in running my simulations and gathering my results.

Finally, I want to thank my friends and family. To my family, Mom, Dad, Tess, Mathew, and Molly, thank you for your endless love and support and for constantly reminding me that hard work and due diligence always pays off. Without your continual support I would not be where I am today. I would also like to thank the truly extraordinary students at the MIT Operations Research Center who not only provided me with lasting friendships but also supported me academically both in the classroom and on this project. 
\vfill
CONTRACT ACKNOWLEDGMENT: This material is based upon work supported by the Air Force under Air Force Contract No. FA8721-05-C-0002 and/or FA8702-15-D-0001. The views expressed in this document are those of the author and do not reflect the official policy or position of the United States Air Force, the United States Department of Defense or the United States Government.